Blocking-resistant communication\\through domain fronting

### 2014-07-15 docs/meek.tex
Note on why you have to be a CDN customer.
Make the arch diagram use the whole width.
Say "address blocking" instead of "endpoint blocking."

@@

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by endpoint.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
Blocking by endpoint is based on \emph{whom you are speaking to},
and blocking by content is based on \emph{what you are saying}.
A skilled censor will do both, and effective circumvention requires meeting both challenges.
An endpoint-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.

@@

The other grand challenge of proxy-based circumvention is endpoint blocking,
against which there have been a few approaches proposed.
Tor has long faced the problem of its entry relays being blocked. The list of
relays is public, so it easy to block all of them by IP address. Tor
bridges~\cite{tor-blocking} are relays that are not universally known, intended
to serve as entry points for censored users. A database of bridges (BridgeDB) seeks to
provide a few secret bridges to anyone who asks, while at the same time making it
difficult to learn the entire list.
The database is accessible over HTTPS and email.
The HTTPS interface requires solving a captcha,
and the email interface responds only to addresses from certain providers, like Gmail,
that have defenses against bulk account creation.
BridgeDB has the feature that repeated queries from the same address
(IP subnet or email address) will receive the same small set of bridges.
Its resistance to enumeration therefore depends both on
having a large number of potential bridges,
and on the censor not being able to control large numbers of IP and email addresses.
BridgeDB is capable of distributing
the addresses of obfsproxy and ScrambleSuit bridges.
The combination
of careful bridge address disbursement and obfuscated protocols
gives Tor's system a realistic claim to addressing both challenges of proxy-based circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time deobfuscation~\cite{foci12-winter}.

Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to endpoint blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
The client must be able to receive a TCP connection; in particular it
may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
There exists a prototype transport that attempts to get both
content-based and endpoint-based blocking resistance by obfuscating traffic
with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
However it is limited because it is not
possible to obfuscate the outermost WebSocket layer;
the censor could decide simply to block all WebSocket.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
System architecture.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure}

@@

The practice of routing traffic through a web service with domain fronting
defeats both endpoint-based blocking and active scanning.
The endpoint (which appears to be the front domain; e.g. www.google.com)
cannot be blocked because to block it would cause collateral damage.
Active scanning is defeated because if the censor accesses the same
endpoint as the client, all they see is a web page served by the front domain.
Even though the censor knows some traffic is being fronted,
by looking only at IP addresses and domain names, it cannot determine which.

>>>>

% CDNs don't route just anywhere---you have to be a customer.

@@

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you are saying},
and blocking by address is based on \emph{whom you are speaking to},
A skilled censor will do both, and effective circumvention requires meeting both challenges.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.

@@

The other grand challenge of proxy-based circumvention is address blocking,
against which there have been a few approaches proposed.
Tor has long faced the problem of its entry relays being blocked. The list of
relays is public, so it easy to block all of them by IP address. Tor
bridges~\cite{tor-blocking} are relays that are not universally known, intended
to serve as entry points for censored users. A database of bridges (BridgeDB) seeks to
provide a few secret bridges to anyone who asks, while at the same time making it
difficult to learn the entire list.
The database is accessible over HTTPS and email.
The HTTPS interface requires solving a captcha,
and the email interface responds only to addresses from certain providers, like Gmail,
that have defenses against bulk account creation.
BridgeDB has the feature that repeated queries from the same address
(IP subnet or email address) will receive the same small set of bridges.
Its resistance to enumeration therefore depends both on
having a large number of potential bridges,
and on the censor not being able to control large numbers of IP and email addresses.
BridgeDB is capable of distributing
the addresses of obfsproxy and ScrambleSuit bridges.
The combination
of careful bridge address disbursement and obfuscated protocols
gives Tor's system a realistic claim to addressing both challenges of proxy-based circumvention.
Address distribution appears to be the weaker side of the defense,
as evidenced by real-world censors' apparent preference for
blocking bridge addresses over real-time deobfuscation~\cite{foci12-winter}.

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
A quirk of the browser proxy model is that the proxy connects to the client rather than the other way around.
The client must be able to receive a TCP connection; in particular it
may not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
There exists a prototype transport that attempts to get both
content-based and address-based blocking resistance by obfuscating traffic
with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
However it is limited because it is not
possible to obfuscate the outermost WebSocket layer;
the censor could decide simply to block all WebSocket.

@@

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
System architecture.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure*}

@@

The practice of routing traffic through a web service with domain fronting
defeats both address-based blocking and active scanning.
The endpoint (which appears to be the front domain; e.g. www.google.com)
cannot be blocked because to block it would cause collateral damage.
Active scanning is defeated because if the censor accesses the same
domain as does the client, all they see is a web page served by the front domain.
Even though the censor knows some traffic is being fronted,
by looking only at IP addresses and domain names, it cannot determine which.
